Activities

### 2025-11-25 activities.qmd
add FK, TP, talk of Gregor (GH 250924)
update (251125, GH)

@@

* Invited session at 70th Annual Meeting of the German Society for Medical Informatics, Biometrics and Epidemiology (Deutsche Gesellschaft für Medizinische Informatik, Biometrie und Epidemiologie e. V., GMDS) in Jena, Germany, 7-11 Sep 2025. Speaker for TG2: Gregor Buch. Topic of the talk: STRATOS Topic Group 2 – Selection of variables and functional forms in multivariable analysis: Results from a review of Covid-19 prognostic models. [Find out more (in German)](https://gmds2025.de/)

>>>>

* Invited talk at the [CFE-CMStatistics 2025](https://www.cmstatistics.org/CFECMStatistics2025) (19th International Joint Conference on Computational and Financial Econometrics and Computational and Methodological Statistics) in London, UK, 13-15 Dec 2025. 
Topic of the session: Researcher degrees of freedom, flexible modeling and interpretability. 
Speaker: Theresa Ullmann. 
Topic of the talk: Comparing methods for flexible estimation of non-linear associations: The importance of suitable performance measures (project TG2-P8).

@@

* Invited session at 70th Annual Meeting of the German Society for Medical Informatics, Biometrics and Epidemiology (Deutsche Gesellschaft für Medizinische Informatik, Biometrie und Epidemiologie e. V., GMDS) in Jena, Germany, 7-11 Sep 2025. Speaker for TG2: Gregor Buch. Topic of the talk: STRATOS Topic Group 2 – Selection of variables and functional forms in multivariable analysis: Results from a review of Covid-19 prognostic models. [Slides](assets/Covid-Modeling-Review_Talk_GMDS2025.pdf)
